Reduced diversity and increased specialization of Alaska salmon fishermen:

### 2017-02-22 salmon/paper/archive/salmon_paper.Rmd
move files

---
title: 'Reduced diversity and increased specialization of Alaska salmon fishermen:
  effects on variation in individual revenues'
author: "Eric, Sean, Ole, Rich, Milo, Jordan, Jen, Alan, others"
date: ''
output:
  html_document: default
  pdf_document:
    fig_caption: yes
  word_document: default
bibliography: CatchPortfolios_salmon.bib
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, tidy=FALSE, tidy.opts=list(width.cutoff=60), warning = FALSE, message = FALSE)
library(knitr)
library(tidyverse)
library(reshape2)
library(date)
library(ggtern)
library(mgcv)
library(fpc)
library(gridExtra)
#library(glmmTMB)
library(zoo)
library(rstan)
modelname = "model-linear" # model-linear-nointeractions

>>>>

---
title: 'Reduced diversity and increased specialization of Alaska salmon fishermen:
  effects on variation in individual revenues'
author: "Eric, Sean, Ole, Rich, Milo, Jordan, Jen, Alan, Ben, etc."
date: '2017-02-08'
output:
  html_document: default
  pdf_document:
    fig_caption: yes
  word_document: default
bibliography: CatchPortfolios_salmon.bib
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, tidy=FALSE, tidy.opts=list(width.cutoff=60), warning = FALSE, message = FALSE)
library(knitr)
library(tidyverse)
library(reshape2)
library(date)
#library(ggtern)
library(mgcv)
#library(fpc)
library(gridExtra)
#library(glmmTMB)
library(zoo)
library(rstan)
library(ggrepel)
modelname = "model-linear" # model-linear-nointeractions
```
